---
  title: "tfidf"
output: html_document
---
  
# TFIDF
This document is some exploratory data analysis of the tweet data I have been scraping. The technique being investigated here is tfidf. tfidf is a metric which helps to find  important words by decreasing the weight for commonly used words and increasing the weight for words that can be specific for the document. I have already built a tool for visualising the most common words each day and so the purpose of this analysis is to find a way to gather useful insights using this new technique.

The code I am using is built upon the work of Kaggle user kailex, in particular his work in this competition:
from kxx https://www.kaggle.com/kailex/r-eda-for-q-gru/code

Some more information on the TFIDF method can be found here:
[TFIDF](https://en.wikipedia.org/wiki/Tf%E2%80%93idf) (short for term frequency–inverse document frequency) 

```{r libraries_and_connections}
suppressMessages(library(tidytext))
suppressMessages(library(stopwords))
suppressMessages(library(tokenizers))
suppressMessages(library(tidyverse))
suppressMessages(library(lubridate))

```

I have previously pulled data relating to 100k tweets from my database and written them to a flat file. This is the data I will be using for this study.

```{r pulling_data}
df <- read_csv("tfidf_analysis_input_df.csv")
df %>% head(10)
```

The first phase in conducting the tfidf analysis is to split the text into individual tokens. During this phase we will also remove unnecessary tokens. For the purposes of this I have removed twitter handles (@handle) and hyperlinks, I finally remove all the non text characters and unnecessary spaces.

```{r splitting data}
tokens <- df %>%
  mutate(question_text = (text %>% 
                            str_replace_all("@[:alpha:]*","") %>% 
                            str_replace_all("http.*","") %>% 
                            str_replace_all("[^[:alpha:][:space:]]+", ""))) %>%  
  unnest_tokens(word, question_text)

tokens %>% 
  group_by(word) %>% tally() %>% arrange(n %>% desc) %>% 
  top_n(10, n)

```

I then join the tokens back on to the original data frame.

```{r}
# tokens <- tokens %>% 
#   anti_join(stop_words, by = "word")

df <- df %>% mutate(status_id = status_id %>% as.numeric)
tokens <- tokens %>% mutate(status_id = status_id %>% as.numeric)


tfidf <- tokens %>%
  dplyr::count(status_id, word, sort = TRUE) %>% 
  bind_tf_idf(word, status_id, n) %>% 
  left_join(df, by = "status_id") %>% as.tbl()

tfidf %>% 
  group_by(date = date(created_at)) %>%
  arrange(tf_idf %>% desc) %>% 
  top_n(30,n)
#need to remove the twitter handles and urls for this to be more useful
```
What we see at this stage is that looking at documents at the tweet level is not particularly interesting because we are looking for words that are common in a particular tweet but not in the whole corpus. A more interesting question may be to ask: what are common words in a particular group of tweets which are uncommon in general. One way to cut this would be by time, e.g. day or hour.


```{r}
df2 <- read_csv("tfidf_analysis_input_df.csv")

df2 %>% 
  select(-c(word_count_aggregated,status_id,search_query)) %>% 
  mutate(day = day(created_at)) %>% 
  group_by(day) %>% 
  summarise(text = paste(text, collapse =" "))



tokens <- df %>%
  mutate(question_text = (text %>% 
                            str_replace_all("@[:alpha:]*","") %>% 
                            str_replace_all("http.*","") %>% 
                            str_replace_all("[^[:alpha:][:space:]]+", ""))) %>%  
  unnest_tokens(word, question_text)

tokens %>% 
  group_by(word) %>% tally() %>% arrange(n %>% desc) %>% 
  top_n(10, n)


df <- df %>% mutate(status_id = status_id %>% as.numeric)
tokens <- tokens %>% mutate(status_id = status_id %>% as.numeric)


tfidf <- tokens %>%
  dplyr::count(status_id, word, sort = TRUE) %>% 
  bind_tf_idf(word, status_id, n) %>% 
  left_join(df, by = "status_id") %>% as.tbl()

tfidf %>% 
  group_by(date = date(created_at)) %>%
  arrange(tf_idf %>% desc) %>% 
  top_n(30,n)


```


```{r}

```

